\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[left=1in,top=1in,right=1in,bottom=1in]{geometry} 
\usepackage[colorlinks=false]{hyperref} % hyper links color
\usepackage{enumitem} % spacing in items
\setlist[itemize]{itemsep = 0.5pt}
\setlist[enumerate]{itemsep = 1pt}

\usepackage[sc]{titlesec} % provide sc font for section


%----------------------------------------------------------------------------------------
%	SECTION FORMATTING
%----------------------------------------------------------------------------------------

\newcommand{\cussection}[1]{\vspace{--0.05in}\section*{#1}\vspace{--0.1in} \hrule\vspace{0.2in} }

%----------------------------------------------------------------------------------------

\title{Mr. \scshape Zihan Wu}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}
\vspace{-0.5in}

%----------------------------------------------------------------------------------
%           Contact Info
%----------------------------------------------------------------------------------
\cussection{Contact}
Position: PhD Candidate in Electrical Engineering, City University of Hong Kong\\
Phone: \texttt{(+852) 9810 6427} or \texttt{(+86) 188 5695 6416} \\ % Your phone number
Email: \texttt{zihanwu7-c@my.cityu.edu.hk} or \texttt{wzh4464@gmail.com}
%----------------------------------------------------------------------------------
%           Education
%----------------------------------------------------------------------------------
\cussection{Education}
\begin{itemize}
    \item Ph.D Candidate in Electrical Engineering, \href{https://www.cityu.edu.hk/}{\emph{City University of Hong Kong}}, Hong Kong SAR, China \hfill 2020--Present
    \item B. S. in Mathematics, \href{https://en.ustc.edu.cn/}{\emph{University of Science and Technology of China}}, Hefei Anhui, China \hfill{2015--2020}
    \item B. S. in Physics, \href{https://en.ustc.edu.cn/}{\emph{University of Science and Technology of China}}, Hefei Anhui, China \hfill{2015--2020}
\end{itemize}



%----------------------------------------------------------------------------------
%           Teaching Experience
%----------------------------------------------------------------------------------

\cussection{Teaching Experience}

\subsection*{Department of Electrical Engineering, City University of Hong Kong}

\begin{itemize}
    \item Topics in Computer Graphics (EE5808) \hfill Spring 2024
    \item Design Project (EE3070) \hfill Fall 2023
    \item Topics in Computer Graphics (EE5808) \hfill Spring 2023
    \item Design Project (EE3070) \hfill Fall 2022
    \item Linear Systems Theory \& Design (EE6620) \hfill Fall 2021
\end{itemize}
%----------------------------------------------------------------------------------
%           Research Experience
%----------------------------------------------------------------------------------

\cussection{Research Experience}

\subsection*{Research Assistant}
Department of Electrical Engineering, City University of Hong Kong \hfill Nov. 2024 -- Present

\subsection*{Tensor Decomposition and Machine Learning}
Research Assistant, City University of Hong Kong Shenzhen Research Institute \hfill Jun. 2020 -- Sep. 2020

\subsection*{Single Molecular Semiconductor based on DNA structure}
Research Assistant, Physics Department, University of Oxford \hfill Jun. 2018 -- Sep. 2018

\subsection*{Academic Paper Contest of Optics}
\begin{itemize}
    \item Head of Gruop: The Design and Research of Optical--Electrical Pulse Detecting System
    \item The First place of USTC \hfill Sep. 2016 -- Nov. 2016
\end{itemize}

\subsection*{China Undergraduate Physics Tournament: Single Lens Telescope}
Group Leader, the First place of USTC \hfill Mar. 2016 -- Jun. 2016

%----------------------------------------------------------------------------------
%          HONORS AND AWARDS
%----------------------------------------------------------------------------------

\cussection{Honors And Awards}



\begin{itemize}
    \item Hong Kong PhD Fellowship Scheme (HKPFS) \hfill 2020--2024
    \item National Encouragement Scholarship, given by the Ministry of Education of the People’s Republic
          of China (top 2\%) \hfill 2017--2018
\end{itemize}

%----------------------------------------------------------------------------------
%          Publications
%----------------------------------------------------------------------------------

\cussection{Publications}

\subsection*{Patents}
\begin{enumerate}
    \item Physical Activity Assessment System And Method -- HK30081186 \hfill May. 2023
\end{enumerate}


\subsection*{Papers}
\begin{enumerate}
    \item Jie Xu, Zihan Wu, Cong Wang, and Xiaohua Jia, ``LMEraser: Large model unlearning via adaptive prompt tuning,'' to appear in \emph{28th International Conference on Artificial Intelligence and Statistics (AISTATS)}, 2025. (Equal contribution first author)
    \item Zihan Wu, Zhaoke Huang, and Hong Yan, ``Scalable co-clustering for large-scale data through dynamic partitioning and hierarchical merging,'' \emph{Proceedings of the 2024 IEEE International Conference on Systems, Man, and Cybernetics}, October 6-10, 2024, Kuching, Sarawak, Malaysia.
    \item Zihan Wu, Zhaoke Huang, and Hong Yan, ``Ellipse detection via global arc compatibilities and adaptive co-clustering for real-world measurement systems,'' accepted by \emph{IEEE Transactions on Instrumentation \& Measurement}, 2024.
    \item Zhaoke Huang, Zihan Wu, and Hong Yan, ``A convex-hull based method with manifold projections for detecting cell protrusions,'' \emph{Computers in Biology and Medicine}, 2024. (Equal contribution first author)
    \item Jie Xu, Yulong Ming, Zihan Wu, Cong Wang, and Xiaohua Jia, ``X-Shard: Optimistic cross-shard transaction processing for sharding-based blockchains,'' \emph{IEEE Transactions on Parallel and Distributed Systems}, 2024.
    \item Jie Xu, Zihan Wu, Cong Wang, and Xiaohua Jia, ``Machine unlearning: Solutions and challenges,'' \emph{IEEE Transactions on Emerging Topics in Computational Intelligence}, 2024.
\end{enumerate}





%----------------------------------------------------------------------------------
%          Publications
%----------------------------------------------------------------------------------

% \cussection{Professional Service}

% \subsection*{Reviewer for Journals \& Conferences}

% \begin{enumerate}
%     \item IEEE Transactions on Intelligent Transportation Systems
% \end{enumerate}

% Skills Certification
% English, Toefl : 107 / 120, Speaking : 23
% Other Skills, C++, Matlab, Get the top level amateur certificate of playing the piano

\cussection{Skills Certification}

\begin{enumerate}
    \item English: TOEFL : 107 / 120, (Speaking : 23)
    \item Other Skills: C++, Matlab, Pytorch
\end{enumerate}

\cussection{Research Interests}

\begin{enumerate}
    \item Machine Learning
    \item Computer Vision
    \item Natural Language Processing
    \item Data Mining
    \item Financial Engineering
\end{enumerate}


\end{document}
